Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-17 paper/paper.tex
update order of important features
tweak section on feature analysis

\begin{itemize}
    \item The proportion of target vertices which are at least distance 3
        apart. We introduced this feature expecting it to be helpful in
        distinguishing between \Glasgow variants: if few vertices are far
        apart, longer paths are unlikely to be useful. However, in practice
        this feature also gives a rough indication of how sparse the graph
        is---locally all-different filtering is weak and expensive on dense
        graphs, and the feature turned out to be helpful for selecting between
        \Glasgow and \LAD variants too;

    \item The mean degree of the target graph;
    \item The maximum degree of the pattern graph;
    \item The number of values removed during \IncompleteLAD presolving;
    \item And the mean degree of the pattern graph, the number of vertices in
        the pattern graph, and the number of vertices in the target graph,
        which were used once each.
\end{itemize}

\noindent This confirms that our decision to consider both the pattern graph
and the target graph for feature extraction was correct, and shows that basic
graph properties do affect the performance of sophisticated filtering
algorithms in reasonably simple ways.

>>>>

\begin{itemize}
    \item the maximum degree of the pattern graph;
    \item the mean degree of the target graph;
    \item the proportion of target vertices that are at least distance 3
        apart;
    \item the number of values removed during \IncompleteLAD presolving.
\end{itemize}

We introduced the proportion of target vertices that are at least 3 apart as a
feature expecting it to be helpful in distinguishing between
\Glasgow variants---if few vertices are far apart, longer paths are unlikely to
be useful. However, in practice this feature also gives a rough indication of
how sparse the graph is---locally all-different filtering is weak and expensive
on dense graphs, and the feature turned out to be helpful for selecting between
\Glasgow and \LAD variants too.

As expected, both the pattern graph and the target graph provide important
features. We also conclude that even basic graph properties are predictive of
sophisticated algorithms' performance.
